|

### 2024-07-11 doc/paper_mine.qmd
adjustment

# Define the relative path to the configuration file
config_path = os.path.join(get_current_path(), '..', 'config', 'config.yaml')
with open(config_path, 'r') as file:
    config = yaml.safe_load(file)

# Extract paths from the config file
STATIC_DATA_PATH = os.path.join(get_current_path(), '..', config['data_paths']['static_data'])
PANEL_DATA_PATH = os.path.join(get_current_path(), '..', config['data_paths']['panel_data'])

>>>>

# Define the relative path to the configuration file
current_path = get_current_path()
project_root = os.path.abspath(os.path.join(current_path, '..'))
config_path = os.path.join(project_root, 'config', 'config.yaml')

# Load the configuration from YAML file
with open(config_path, 'r') as file:
    config = yaml.safe_load(file)

# Extract paths from the config file
STATIC_DATA_PATH = os.path.join(project_root, 'data', 'external', 'wscp_static.txt')
PANEL_DATA_PATH = os.path.join(project_root, 'data', 'external', 'wscp_panel.xlsx')
